---
title: "PS7 EDA"
author: "STAT 139 (Fall 2024) Teaching Team"
date: "Due Friday, November 15, 2024 at 11:59pm"
output: pdf_document
urlcolor: blue
---

Each important continuous variable in your dataset reports:

- The number of non-missing observations

- The  number of missing observations

- A measure(s) of the central tendency (i.e., mean, media)

- A measure(s) of variability (i.e, sd, IQR)

and for each important categorical variable in your dataset reports:

- The levels of the variable

- For each level:
  
  - The number of non-missing observations
  
  - The number of missing observations

```{r}
library(dplyr)
library(knitr)
library(tidyr)

cycles<-read.csv("data/physiological_cycles.csv") 
sleep <- read.csv("data/sleeps.csv")
workouts <- read.csv("data/workouts.csv")
```

# 1 - Data Cleaning

## 1.1 - Clean Physio

```{r}
str(cycles)


# Convert date-time columns to POSIXct format
cycles$Cycle.start.time <- as.POSIXct(cycles$Cycle.start.time, format="%Y-%m-%d %H:%M:%S", tz="UTC")
cycles$Cycle.end.time <- as.POSIXct(cycles$Cycle.end.time, format="%Y-%m-%d %H:%M:%S", tz="UTC")
cycles$Sleep.onset <- as.POSIXct(cycles$Sleep.onset, format="%Y-%m-%d %H:%M:%S", tz="UTC")
cycles$Wake.onset <- as.POSIXct(cycles$Wake.onset, format="%Y-%m-%d %H:%M:%S", tz="UTC")

# Calculate duration in hours
cycles$Cycle.duration <- difftime(cycles$Cycle.end.time, cycles$Cycle.start.time, units = "hours")
cycles$Sleep.duration <- difftime(cycles$Wake.onset, cycles$Sleep.onset, units = "hours")

# Convert duration to numeric
cycles$Cycle.duration <- as.numeric(cycles$Cycle.duration)
cycles$Sleep.duration <- as.numeric(cycles$Sleep.duration)

# Summary of continuous variables
cycles_continuous_summary <- cycles %>%
  select_if(is.numeric) %>%
  summarise_all(list(
    non_missing = ~sum(!is.na(.)),
    missing = ~sum(is.na(.)),
    mean = ~mean(., na.rm = TRUE),
    median = ~median(., na.rm = TRUE),
    sd = ~sd(., na.rm = TRUE),
    IQR = ~IQR(., na.rm = TRUE)
  ))

cycles_continuous_summary_long <- cycles_continuous_summary %>%
  pivot_longer(cols = everything(),
               names_to = c("Variable", "Metric"),
               names_sep = "_",
               values_to = "Value") %>%
  pivot_wider(names_from = "Metric", values_from = "Value")

# Display the summary
kable(cycles_continuous_summary_long)
```

## 1.2 - Clean Sleep

```{r}
str(sleep)

# Convert date-time columns to POSIXct format
sleep$Cycle.start.time <- as.POSIXct(sleep$Cycle.start.time, format="%Y-%m-%d %H:%M:%S", tz="UTC")
sleep$Cycle.end.time <- as.POSIXct(sleep$Cycle.end.time, format="%Y-%m-%d %H:%M:%S", tz="UTC")
sleep$Sleep.onset <- as.POSIXct(sleep$Sleep.onset, format="%Y-%m-%d %H:%M:%S", tz="UTC")
sleep$Wake.onset <- as.POSIXct(sleep$Wake.onset, format="%Y-%m-%d %H:%M:%S", tz="UTC")

# Calculate duration in hours
sleep$Cycle.duration <- difftime(sleep$Cycle.end.time, sleep$Cycle.start.time, units = "hours")
sleep$Sleep.duration <- difftime(sleep$Wake.onset, sleep$Sleep.onset, units = "hours")

# Convert duration to numeric
sleep$Cycle.duration <- as.numeric(sleep$Cycle.duration)
sleep$Sleep.duration <- as.numeric(sleep$Sleep.duration)

# Summary of continuous variables
sleep_continuous_summary <- sleep %>%
  select_if(is.numeric) %>%
  summarise_all(list(
    non_missing = ~sum(!is.na(.)),
    missing = ~sum(is.na(.)),
    mean = ~mean(., na.rm = TRUE),
    median = ~median(., na.rm = TRUE),
    sd = ~sd(., na.rm = TRUE),
    IQR = ~IQR(., na.rm = TRUE)
  ))

# Reshape the summary table to a longer format and then back to wide format for readability
sleep_continuous_summary_long <- sleep_continuous_summary %>%
  pivot_longer(cols = everything(),
               names_to = c("Variable", "Metric"),
               names_sep = "_",
               values_to = "Value") %>%
  pivot_wider(names_from = "Metric", values_from = "Value")

# Display the summary in a readable table format
kable(sleep_continuous_summary_long)


# Summarize the 'Nap' categorical variable
sleep_categorical_summary <- sleep %>%
  group_by(Nap) %>%
  summarise(
    non_missing = sum(!is.na(Nap)),
    missing = sum(is.na(Nap))
  )

# Display the summary
print(sleep_categorical_summary)


```


## 1.3 - Clean Workouts

```{r}
str(workouts)

# Convert date-time columns to POSIXct format
workouts$Cycle.start.time <- as.POSIXct(workouts$Cycle.start.time, format="%Y-%m-%d %H:%M:%S", tz="UTC")
workouts$Cycle.end.time <- as.POSIXct(workouts$Cycle.end.time, format="%Y-%m-%d %H:%M:%S", tz="UTC")
workouts$Workout.start.time <- as.POSIXct(workouts$Workout.start.time, format="%Y-%m-%d %H:%M:%S", tz="UTC")
workouts$Workout.end.time <- as.POSIXct(workouts$Workout.end.time, format="%Y-%m-%d %H:%M:%S", tz="UTC")

# Calculate duration in hours
workouts$Cycle.duration <- difftime(workouts$Cycle.end.time, workouts$Cycle.start.time, units = "hours")
workouts$Workout.duration <- difftime(workouts$Workout.end.time, workouts$Workout.start.time, units = "hours")

# Convert duration to numeric
workouts$Cycle.duration <- as.numeric(workouts$Cycle.duration)
workouts$Workout.duration <- as.numeric(workouts$Workout.duration)

# Summary of continuous variables
workouts_continuous_summary <- workouts %>%
  select_if(is.numeric) %>%
  summarise_all(list(
    non_missing = ~sum(!is.na(.)),
    missing = ~sum(is.na(.)),
    mean = ~mean(., na.rm = TRUE),
    median = ~median(., na.rm = TRUE),
    sd = ~sd(., na.rm = TRUE),
    IQR = ~IQR(., na.rm = TRUE)
  ))

# Reshape the summary table to a longer format and then back to wide format for readability
workouts_continuous_summary_long <- workouts_continuous_summary %>%
  pivot_longer(cols = everything(),
               names_to = c("Variable", "Metric"),
               names_sep = "_",
               values_to = "Value") %>%
  pivot_wider(names_from = "Metric", values_from = "Value")

# Display the summary in a readable table format
kable(workouts_continuous_summary_long)

# Print the table in a readable format
kable(workouts_continuous_summary_long)


# Summarize the 'GPS.enabled' categorical variable
gps_summary <- workouts %>%
  group_by(GPS.enabled) %>%
  summarise(
    non_missing = sum(!is.na(GPS.enabled)),
    missing = sum(is.na(GPS.enabled))
  )

# Summarize the 'Activity.name' categorical variable
activity_summary <- workouts %>%
  group_by(Activity.name) %>%
  summarise(
    non_missing = sum(!is.na(Activity.name)),
    missing = sum(is.na(Activity.name)),
    count = n()
  )

# Display the summaries
print(gps_summary)
print(activity_summary)


```

# 2 - Jonas EDA

